The effects of varying depth in cosmic shear surveys

### 2019-10-04 paperdraft.tex
changes

One systematic effect is the variation of depth in a survey. While effects like Galactic extinction or dithering strategies do play a role in every survey, this work focuses on the effects caused by varying atmospheric conditions that are found in ground-based surveys. To first order, this variation can be modelled by a piece-wise constant depth function, which varies from pointing to pointing. In this work we assume the specifications of the Kilo-Degree Survey \citep[KiDS,][]{Kuijken:2015}, namely an assembly of $1\,\text{deg}^2$ square fields.

@@

An inspection of KiDS-data showed that the redshift distribution of sources is highly correlated with the depth in the $r$-band. We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, i.e. if a pointing had a shallower depth than 90\% of the other pointings, it would belong to the first percentile, and so on. For each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and a source redshift distribution $p^i_m(z)$ following the direct spectroscopic calibration method of H18. In Fig.~\ref{fig:nz_of_meanz} the average redshift and weighted number of galaxies are plotted for each percentile of each redshift bin, whereas a selection of source redshift distributions is depicted in Fig.~\ref{fig:nofz_percentiles}. A table of the limiting magnitudes for each percentile can be found in Tab.~\ref{tab:maglim}.
%
\begin{figure}
\centering
\includegraphics[trim = {1cm 0 1.2cm 0.1cm}, clip, width=\linewidth]{images/dist_z_all.pdf}
\caption{The source redshift distributions $p^i_m(z)$ for the best, average, and worst percentile in each tomographic redshift bin.}
\label{fig:nofz_percentiles}
\end{figure}
% Asserting an arbitrary cosmological model, we can transform the source redshift distributions $p^i_m(z)$ into comoving distance probability distributions $\mathcal{L}^i_m(\chi)$.

>>>>

One systematic effect is the variation of depth in a survey. While effects like Galactic extinction or dithering strategies do play a role in every survey, this work focuses on the effects caused by varying atmospheric conditions that are found in ground-based surveys. To first order, this variation can be modelled by a piece-wise constant depth function, which varies from pointing to pointing. In this work we assume the specifications of the Kilo-Degree Survey \citep[KiDS,][]{Kuijken:2015}, namely an assembly of $1\,\text{deg}^2$ square fields. To quantify the depth, we chose the limiting magnitude of the $r$-band, as defined in \citet{2017A&A...604A.134D}, since it serves as the detection band and is thus most important for determining source galaxies.

@@

An inspection of KiDS-data showed that the redshift distribution of sources is highly correlated with the limiting magnitude in the $r$-band. We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, i.e. if a pointing had a shallower depth than 90\% of the other pointings, it would belong to the first percentile, and so on. For each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and a source redshift distribution $p^i_m(z)$ following the direct spectroscopic calibration method of H18. In Fig.~\ref{fig:nz_of_meanz} the average redshift and weighted number of galaxies are plotted for each percentile of each redshift bin, whereas a selection of source redshift distributions is depicted in Fig.~\ref{fig:nofz_percentiles}. A table of the limiting magnitudes for each percentile can be found in Tab.~\ref{tab:maglim}.
%
\begin{figure}
\centering
\includegraphics[trim = {1cm 0 1.2cm 0.1cm}, clip, width=\linewidth]{images/dist_z_all.pdf}
\caption{The source redshift distributions $p^i_m(z)$ for the best, average, and worst percentile in each tomographic redshift bin.}
\label{fig:nofz_percentiles}
\end{figure}
% Asserting an arbitrary cosmological model, we can transform the source redshift distributions $p^i_m(z)$ into comoving distance probability distributions $\mathcal{L}^i_m(\chi)$.
